Transforming Trash as an Artistic Act

### 2016-01-08 chapter4_reduced.tex
fixing errors
Former-commit-id: cb1fa634f5502bfce534528cc9f2324c88009894

%[disposable paper, packaging]
Collected items are mainly disposables ones. Most of them are paper or made from paper. The word paper comes from papyrus, the plant that was first used for writing in ancient Egypt long before the making of paper in China. In modern times all types and qualities of paper such as newspaper paper, print paper, and carton used for boxes pass through the same basic method of manufacture \citep{trafford2012paper}. It is fundamental medium for writing, reading, education, communication, information storage and many others. Its role in the development of human civilization can not be neglected. (Paper in several forms is consumed on a daily basis \cite{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people. On the other hand for artist it offers great diversity in order to make compositions as can be seen in the works of collage. Further it is easy to find and collect them. Even if it is thrown out, still appropriate for painting and writing.

@@

% TODO refre
\begin{quote}
Take a newspaper.\\
Take some scissors.\\
Choose from this paper an article the length you want to make your poem.\\
Cut out the article.\\
Next carefully cut out each of the words that make up this article and put them all in a bag.\\
Shake gently.\\
Next take out each cutting one after the other.\\
Copy conscientiously in the order in which they left the bag.\\
The poem will resemble you.\\
And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}

@@

@@

Beyond all of these for the audience the story of the collected materials is a mystery. Audience are not aware from all of these written in this thesis. I want to reveal the act behind these notebooks. For that reason a website that store the records of collected materials can be helpful. They can visit there anytime. The other other reason that I select to website is I am fluent in web development.

%
%
\section{Parts of the Final Work}
% The development progress result in different part of the objects.
As also can be understood by the previous section the project introduced in this thesis have different parts. Each part support the other. They are connected with each other. Different parts lead different inquiries.

@@

Notebooks have been used for different purposes such as drawing, writing and recording, ideas or memoranda by many artists, scientists, and thinkers through the ages. Further same exist for me and people around me. Although the digital alternatives of it paper maintains its place in the community.

@@

Every notebook has unique serial and with this it can be tracked down when it was produced and which materials are used production of it. Serial is generated through the first letter of composed metarial.

@@

\begin{figure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
    \end{subfigure}
    \caption{Example placement at Bilkent}
    \label{fig:ExperimentWithPaper}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
    \end{subfigure}
    \caption{Example placement at Torun}
    \label{fig:ExperimentWithPaper}
\end{figure}

@@

%
%
\subsection{Website}
As I think that finding a place to the discarded items is one of the main purposes of this project. As it finds a place in people's life again, it also finds another place in the digital space.

Mainly websites displays the (hi)story of notebooks. Further it is a place to track the journey the notebooks. As I claimed that it is not a finished work. Transformation of it does not completed. It always continues. Therefore a website that anyone can reach and share their progress via website  Anyone can later discover how they turned to new things.

As I leave notebooks different places I do not have connection with people who take them. This website also will help to collect/share peoples ideas about the notebooks.

It will contain a section for how notebooks are produced and the story behind it. The purpose is to record the creative process and share with the others. Revealing the process is significant to demystifiying the truth about the project. It makes it more clear that the object used here is actually transformed from something else.

@@

% [Why website] (database, establishing communication, tracking in time) It was not only that such characteristic was clearly suited for the exploration of human spaces such as home, but it was also that I am comfortably and confidently fluent in coding and web development.

Website can be accessible through the this address http:\\kulu.be\\notebook-project. Domain name kulu.be belongs to me and project placed under a directory of it. Website is coded by me with the common and trusted open source libraries and frameworks. Its code also available at this address. Site is served from GitHub pages which provides free website hosting. Pages are generated by Jekyll which is a static website generator through it some repetitive works are can be easily automatized.

People can access to images and descriptions of notebooks. All the development process of the project will be revealed in this website. Will contain list of collected materials.

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
  \caption{QR Code sample}
  \label{fig:Banner_1}
\end{figure}

@@

All the progress up to now forms the core of the project. However it is not limited with it. The project will be continued after this thesis completed. New features will be added to the website. In the future it is planned that through the website people can be able to request to get notebooks. Thus project becomes more accessible to the other people. Moreover notebooks done by others from trash can be added to the website. Beyond notebooks various objects transformed from trash can find a place in the website.

% MAYBE LATER
% transformation practices...
% Notebooklar insanın yanında kolayca taşınabildiği için aslında bir yandan fikri yaymak için ideal. Zaten showing off'un ne kadar önemli olduğu rubbish theoryde söylenmişti.

% their dimensions matches.
In the production phase of the boxes, I discovered that my folded notebooks are fit into the many cardboxes. In other words dimensions of them are not very different. This property of items make the production easy. System supports the reuse of the object with less effort in this way.

At first I often cut the paper to match the dimensions of notebooks but later only folding gives the same result. Thus I can preserve their state. While turning objects to the notebooks I tried to be preserve their look and feel. Olabildigince az mudahelede bulundum. Bu sekilde onceki halleri hakkinda daha cok fikir sahibi olunabilir. Ben copleri taninir halde birakmak istiyordum. Neredeyse olduklari gibi biraktim. Gerisini onu kullananlara biraktim.

>>>>

%[disposable paper, packaging]
Collected items are mainly disposables ones. Most of them are paper or made from paper. The word paper comes from papyrus, the plant that was first used for writing in ancient Egypt long before the making of paper in China. In modern times all types and qualities of paper such as newspaper paper, print paper, and carton used for boxes pass through the same basic method of manufacture \citep{trafford2012paper}. It is fundamental medium for writing, reading, education, communication, information storage and many others. Its role in the development of human civilization can not be neglected. (Paper in several forms is consumed on a daily basis \citep{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people. On the other hand for artist it offers great diversity in order to make compositions as can be seen in the works of collage. Further it is easy to find and collect them. Even if it is thrown out, still appropriate for painting and writing.

@@

% TODO refre
\begin{quote}
Take a newspaper. Take some scissors. Choose from this paper an article the length you want to make your poem. Cut out the article. Next carefully cut out each of the words that make up this article and put them all in a bag. Shake gently. Next take out each cutting one after the other. Copy conscientiously in the order in which they left the bag. The poem will resemble you. And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}

@@

% TODO boxes and wooden cases
To hold notebooks together I made several small boxes from discarded card boxes. Notebooks are put inside of them.

In the production phase of the boxes, I discovered that my folded notebooks are fit into the many card boxes. In other words dimensions of them are not very different. This property of items make my production more easier. It shows that industrial system supports the reuse of the object with less effort in this way.

% Rubbish Theory showing off.

@@

Beyond all of these for the audience the story of the collected materials is a mystery. Audience are not aware from all of these written in this thesis. I want to reveal the act behind these notebooks. However there is a lot information that can not be fit into the pages of notebooks. For that reason such problems was clearly solved through a website that store the records of notebooks and collected materials. They can visit there anytime. The other other reason that I select to website is I am comfortably and confidently fluent in coding and web development.

%
%
\section{Parts of the Final Work}
As also can be understood by the previous section the project introduced in this thesis have different parts. Each part support the other. They are connected with each other. Different parts lead different inquiries.

@@

Notebooks have been used for different purposes such as drawing, writing and recording, ideas or memorandum by many artists, scientists, and thinkers through the ages. Further same exist for me and people around me. Although the digital alternatives of it paper maintains its place in the community.

@@

Every notebook has unique serial and with this it can be tracked down when it was produced and which materials are used production of it. Serial is generated through the first letter of composed material.

@@

\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
    \caption{Library}
    \label{fig:BilkentLibrary}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
    \caption{Computer Laboratory}
    \label{fig:BilkentLaboratory}
  \end{minipage}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
    \end{subfigure}
    \caption{Sample placement at Torun}
    \label{fig:ExperimentWithPaper}
\end{figure}

@@

%
%
\subsection{Website}
Finding a new place to the discarded items is one of the main purposes of this project. Not only it finds a place in people's life again, but also it finds another place in the digital space.

Mainly website displays the (hi)story of notebooks. It contains a section for how notebooks are produced and the story behind it. The purpose is to record the creative process and share with others. Revealing the process is significant to demystifiying the truth about the project. It makes it more clear that the object used here is actually transformed from something else. People can access to images and descriptions of notebooks. All the development process of the project will be revealed in this website. Will contain list of collected materials.

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
  \caption{Sample of QR code and notebook serial}
  \label{fig:Banner_1}
\end{figure}

Website is a place to track the journey the notebooks. Transformation of it does not completed. It always continues. Therefore a website that anyone can reach and share their progress via website will show their evolution in time. Anyone can later discover how they turned to new things.

As I leave notebooks different places I do not have connection with people who take them. This website also will help to share peoples ideas about the notebooks.

@@

Website can be accessible through this address http:\textbackslash\textbackslash kulu.be\textbackslash notebook-project. Domain name kulu.be belongs to me and project placed under a directory of it. Website is coded by me with the common and trusted open source libraries and frameworks. Its code also available at this address. Site is served from GitHub pages which provides free website hosting. Pages are generated by Jekyll which is a static website generator through it some repetitive works are can be easily automatized.

@@

All the progress up to now forms the core of the project. However it is not limited with it. The project will be continued after this thesis completed. New features will be added to the website. In the future it is planned that through the website people can be able to request to get notebooks. Thus notebooks become more accessible to the other people. Moreover notebooks done by others from trash can be added to the website. Beyond notebooks various objects transformed from trash can find a place in the website.
